MG7: Configurable and scalable 16S data analysis

### 2016-07-26 docs/mg7-paper/out/paper.tex
note about fixing LCA figure

All the reads are assigned under two different algorithms of assignment:
i. Lowest Common Ancestor based taxonomic assignment (LCA) and ii. Best
BLAST Hit based taxonomic assignment (BBH). Figure 2 displays
schematically the LCA algorithm applied sensu stricto (left panel) and
the called `in line' exception (right panel) designed in order to gain
specificity in the assignments in the cases in which the topology of the
taxonomical nodes corresponding to the BLAST hits support sufficiently
the assignment to the most specific taxon.

\begin{figure}[htbp]
\centering
\includegraphics{./Figure-2.jpg}
\caption{\textbf{Lowest Common Ancestor algorithm for taxonomic
assignment.} The Left panel displays an example of the application of
LCA algorithm in a \emph{sensu stricto} mode. A, B, C and D represent
taxonomy tree nodes with assigned reads. Right panel displays the
\emph{in line} mode of assignment which is an exception for the
\emph{sensu stricto} mode of application of LCA algorithm. The \emph{in
line} mode is used when all the nodes are located in a line without
bifurcations. In that case the taxon assigned is the most specific (the
most distant from the root).}
\end{figure}

\paragraph{Lowest Common Ancestor based Taxonomic
Assignment}\label{lowest-common-ancestor-based-taxonomic-assignment}

>>>>

All the reads are assigned under two different algorithms of assignment:
i. Lowest Common Ancestor based taxonomic assignment (LCA) and ii. Best
BLAST Hit based taxonomic assignment (BBH). Figure 2 displays
schematically the LCA algorithm.

\begin{figure}[htbp]
\centering
\includegraphics{./Figure-2.jpg}
\caption{\textbf{Lowest Common Ancestor algorithm for taxonomic
assignment.} \textbf{TODO UPDATE THIS FIGURE!} The Left panel displays
an example of the application of LCA algorithm in a \emph{sensu stricto}
mode. A, B, C and D represent taxonomy tree nodes with assigned reads.
Right panel displays the \emph{in line} mode of assignment which is an
exception for the \emph{sensu stricto} mode of application of LCA
algorithm. The \emph{in line} mode is used when all the nodes are
located in a line without bifurcations. In that case the taxon assigned
is the most specific (the most distant from the root).}
\end{figure}

\paragraph{LCA Assignment}\label{lca-assignment}
